\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-10 chapters/3_algorithm.tex
Add image, small changes

\paragraph{Sum Linkage} -- 
On signed graphs, the sum of two attractive (or repulsive) interactions is still attractive (repulsive). On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable. This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on positive weighted graphs. On signed graphs, such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}. All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged. But only GAEC always makes the \emph{greedy-choice} that will mostly decrease the multicut objective at every step. The authors of \cite{levinkov2017comparative} also proposed a version of GAEC with cannot-link constraints named \emph{GreedyFixation}, but the constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) did perform better in our experiments.

>>>>

\paragraph{Sum Linkage} -- 
On signed graphs, the sum of two attractive (or repulsive) interactions is still attractive (repulsive). On the other hand, on positive weighted graphs, a strong attractive interaction could be obtained by summing many weak interactions, which is often not desirable \TODO{Update}. This explains why, to our knowledge, an agglomerative algorithm with sum linkage has never been used on positive weighted graphs. On signed graphs, such an algorithm was pioneered in \cite{levinkov2017comparative,keuper2015efficient} and was named Greedy Agglomerative Edge Contraction (GAEC)\footnote{An algorithm equivalent to GAEC was recently independently re-proposed in \cite{chehreghani2020hierarchical}.}. All variations of \algname{} decrease the multicut objective defined in Eq.~\ref{eq:MC_objective} each time two clusters with positive interaction are merged. But only GAEC always makes the \emph{greedy-choice} that will mostly decrease the multicut objective at every step. The authors of \cite{levinkov2017comparative} also proposed a version of GAEC with cannot-link constraints named \emph{GreedyFixation}, but the constrained sum-link version of \algname{} proposed here (named \emph{HCC-Sum} in Table~\ref{tab:linkage-criteria}) did perform better in our experiments.

### 2021-03-10 chapters/5_experiments_intro.tex
Add image, small changes

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}). It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how \emph{MWS} can achieve competitive performances with considerably lower runtimes.

>>>>

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, where every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}). It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how \emph{MWS} can achieve competitive performances with considerably lower runtimes.
